Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-06 src/paper.tex
update

@@

    \renewcommand{\arraystretch}{1.2}
    \begin{center}
        \begin{tabular}{ccccccc}
            \Xhline{2\arrayrulewidth} % Bold top line
            \multirow{2}{*}{SSL-Model} & \multirow{2}{*}{Type} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
            \cline{3-5}
                                                       &                             & SIG     & BAK     & OVL    &                       &                          \\ 
            \hline
            \multirow{2}{*}{Hubert}                              &  Discrete                          & 3.56    & 4.09    & 3.30   & 81.3\%                & 0.865\_d                        \\
                                             &  Hybrid                          & 3.57    & 4.10    & 3.32   & 35.1\%                & 0.907\_d                        \\
            \hline
            \multirow{2}{*}{WavLM-L6}                              &  Discrete                          & 2.08    & 2.07    & 1.64   & 122.1\%                & 0.589\_d                        \\
            &  Hybrid                          & 3.54    & 3.84    & 3.12   & 30.0\%                & 0.849\_d                        \\
            \hline
            \hline
            \multirow{2}{*}{WavLM}                                     &  Discrete                          & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d                        \\
                                              &  Hybrid                          & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                        \\

            \Xhline{2\arrayrulewidth} % Bold top line              
            \end{tabular}
            \label{abla_1}

      \end{center}
      \caption{Iwdad}
      \vspace{-25pt}
    \end{table}

@@

>>>>

    \renewcommand{\arraystretch}{1.2}
    \begin{center}
        \begin{tabular}{ccccccc}
            \Xhline{2\arrayrulewidth} % Bold top line
            \multirow{2}{*}{SSL-Model} & \multirow{2}{*}{Type} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
            \cline{3-5}
                                                       &                             & SIG     & BAK     & OVL    &                       &                          \\ 
            \hline
            \multirow{2}{*}{HuBERT}                              &  Discrete                          & 3.56    & 4.09    & 3.30   & 81.3\%                & 0.865\_d                        \\
                                             &  Hybrid                          & 3.57    & 4.10    & 3.32   & 35.1\%                & 0.907\_d                        \\
            \hline
            \multirow{2}{*}{WavLM-L6}                              &  Discrete                          & 2.08    & 2.07    & 1.64   & 122.1\%                & 0.589\_d                        \\
            &  Hybrid                          & 3.54    & 3.84    & 3.12   & 30.0\%                & 0.849\_d                        \\
            \hline
            \hline
            \multirow{2}{*}{WavLM}                                     &  Discrete                          & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d                        \\
                                              &  Hybrid                          & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                        \\

            \Xhline{2\arrayrulewidth} % Bold top line              
            \end{tabular}
            \linebreak
            \caption{Performance of different SSL models and layer selections. HuBERT model subsitutes the WavLM Large to HuBERT Large as the SSL model.
            The WavLM-L6 uses only the 6th layer of hidden output of WavLM Large. WavLM denotes our TSELM model which uses 6 different output layers. 
            }
            \label{hubert_wavlm_6}
      \end{center}
      \vspace{-25pt}
    \end{table}

@@

@@

In Table \ref{hubert_wavlm_6}, we have compared the performance of different SSL models and the selection between one layer or multiple layers to discretize. 
Our results have shown that the using HuBERT as SSL model has achieved better DNSMOS scores but with worse dWER compared to our WavLM baseline.
The better DNSMOS scores might be related to the vocoders but it does not reflect the speech intelligibility which is important in speech separation. 
For dWER, this might be because that HuBERT is trained on clean speech and that it might not capture the rich speech information of mixed speeches. 
Our results from WavLM-L6 have shown that for speech separation, using multiple layers to discretize is better than using only one layer.

Finally, we have observed a performance gap between discrete methods and continuous methods.
